Demystifying the Computer Science Ph.D. Admission in the US \\{\Large A guide for Vietnamese and International Students

### 2023-06-11 phd-cs-us.tex
updates

So what can you do about this? several things such as asking your CS dept to put itself on CSRankings (it's the easiest way to get CS people to know about the school), explaining about your school in your statement (and asking your LOR writer to do that too), and of course, if you're Vietnamese, considering a CS PhD program that has \href{https://github.com/dynaroars/dynaroars.github.io/wiki/Viet-CS-Profs-US}{Vietnamese professors}.

\begin{commentbox}
Vu: Sometime PhD admission committee will share a document such as \href{https://github.com/dynaroars/dynaroars.github.io/wiki/Foreign-Top-Schools}{this one}, which lists the top schools in several countries. I have looked at Vietnamese applications (whether they are assigned to me or not) and provide inputs to the reviewers of those applications, e.g., X is the top tech school in Vietnam and so it should be \emph{top} instead of \emph{unknown} foreign, which makes a huge difference.
\end{commentbox}

@@

  \begin{table}[h!]
    \centering
    \small
    \caption{Top 50 CS PhD programs in the U.S. (CSRankings, June 2023)}\label{tab:ranking}
  \begin{tabular}{rl|rl}
    \toprule
    1 & Carnegie Mellon & 26 & Univ. of California - Irvine \\
    2 & Univ. of Illinois at Urbana-Champaign  & 27 &  Duke University \\
    3 & Univ. of California-San Diego & 28 & Rutgers University \\
    4 & MIT & 29 & Univ. of California - Riverside\\
    5 & Georgia Institute of Technology         & 30 & Northwestern University\\
    6 & Stanford University& 31 & Pennsylvania State University  \\
    7 & University of Michigan - Ann Arbor   & 32& George Mason University\\  
    8 & University of Washington      &33 &  Harvard University \\
    9 &  Univ. of California - Berkeley  &34&  Univ. of California - Santa Cruz \\
    10 & Cornell University  & 35 &  Yale University \\
    11 & University of Maryland - College Park &  36& Brown University \\ 
    12 & Northeastern University 37&  Ohio State University\\
    13 & University of Wisconsin - Madison  &38& Texas A\&M University \\
    14 & Columbia University   &39 & Boston University  \\
    15 &   Purdue University  &40& North Carolina State University\\\  
    16 & University of Texas at Austin   &41 & University of Utah \\
    17 & University of Pennsylvania &42 & University at Buffalo\\
    18 & Princeton University  & 43& Rice University\\
    19 & University of Massachusetts-Amherst & 44&  University of Colorado-Boulder \\
    20 &  New York University  &45& University of Illinois at Chicago  \\
    21 & Univ. of California - Los Angeles &46& Virginia Tech  \\
    22 & University of Southern California &47&  Arizona State University \\
    23 & Stony Brook University &48&University of Minnesota \\
    24 & University of Chicago &49& University of Virginia \\
    25 & Univ. of California - Santa Barbara &50& University of North Carolina \\
    \bottomrule
    \end{tabular}
\end{table}

>>>>

So what can you do about this? several things such as asking your CS dept to put itself on CSRankings (it's the easiest way to get CS people to know about the school), explaining about your school in your statement (and asking your LOR writer to do that too), and of course, if you're interested in working with Vietnamese professors, consider a PhD program in the US that  \href{https://github.com/dynaroars/dynaroars.github.io/wiki/Viet-CS-Profs-US}{have them}.

\begin{commentbox}
Vu: Sometime PhD admission committee will share a document such as \href{https://github.com/dynaroars/dynaroars.github.io/wiki/Foreign-Top-Schools}{this one}, which lists the top schools in several countries. I have looked at Vietnamese applications (whether they are assigned to me or not) and provide input to the reviewers of those applications, e.g., X is the top tech school in Vietnam and so it should be \emph{top} instead of \emph{unknown} foreign, which makes a huge difference.
\end{commentbox}

@@

  \begin{table}[h!]
    \centering
    \small
    \caption{Top 50 CS PhD programs in the U.S. (CSRankings, June 2023)}\label{tab:ranking}
  \begin{tabular}{rl|rl}
    \toprule
    1 & Carnegie Mellon & 26 & Univ. of California - Irvine \\
    2 & Univ. of Illinois at Urbana-Champaign  & 27 &  Duke University \\
    3 & Univ. of California-San Diego & 28 & Rutgers University \\
    4 & MIT & 29 & Univ. of California - Riverside\\
    5 & Georgia Institute of Technology         & 30 & Northwestern University\\
    6 & Stanford University& 31 & Pennsylvania State University  \\
    7 & University of Michigan - Ann Arbor   & 32& George Mason University\\  
    8 & University of Washington      &33 &  Harvard University \\
    9 &  Univ. of California - Berkeley  &34&  Univ. of California - Santa Cruz \\
    10 & Cornell University  & 35 &  Yale University \\
    11 & University of Maryland - College Park &  36& Brown University \\ 
    12 & Northeastern University &37&  Ohio State University\\
    13 & University of Wisconsin - Madison  &38& Texas A\&M University \\
    14 & Columbia University   &39 & Boston University  \\
    15 &   Purdue University  &40& North Carolina State University\\\  
    16 & University of Texas at Austin   &41 & University of Utah \\
    17 & University of Pennsylvania &42 & University at Buffalo\\
    18 & Princeton University  & 43& Rice University\\
    19 & University of Massachusetts-Amherst & 44&  University of Colorado-Boulder \\
    20 &  New York University  &45& University of Illinois at Chicago  \\
    21 & Univ. of California - Los Angeles &46& Virginia Tech  \\
    22 & University of Southern California &47&  Arizona State University \\
    23 & Stony Brook University &48&University of Minnesota \\
    24 & University of Chicago &49& University of Virginia \\
    25 & Univ. of California - Santa Barbara &50& University of North Carolina \\
    \bottomrule
    \end{tabular}
\end{table}
